Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-02-21 paper/structureScene.tex
restrucutre experiments
new baseline figure

The \emph{RbQ} measures are compared to commonly used early integration approach \emph{early}, which consists in averaging over time the feature set of each scene, resulting in one feature vector per scene. The distance on this average feature vector is then used to determine $p@k$. For the BOF approach of Aucouturier et al. \cite{aucouturier2007bag}, $10$-component GMMs are estimated for each scene using the expectation-maximization (EM) algorithm \cite{dempster-laird}. The similarity between a given pair of scene GMMs is then calculated through Monte Carlo sampling approximation. To ensure convergence of the EM algorithm for the scattering features, we reduce their dimension from $1367$ to $30$ by projecting the features onto the top $30$ principal components of the dataset.

@@

% \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{figures/lostanlen}}]{Vincent Lostanlen} was born in 1992. He received an engineering degree from TELECOM ParisTech in 2013 and his M.S. degree in acoustics, signal processing, and musical informatics (ATIAM) from the Universit\'{e} Pierre et Marie Curie (UPMC) and the Ircam in Paris, France, in 2013. Since 2013, he is a Ph.D. student at \'{E}cole normale sup\'{e}rieure in Paris, working under the supervision of St\'{e}phane Mallat. His research focuses on defining convolutional operators in the time-frequency domain with applications in audio classification.
% \end{IEEEbiography}
%
% \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{figures/lafay}}]{Gr\'egoire Lafay} was born in 1990. He received the B.S. degree in Acoustic from the University Pierre and Marie Curie (UPMC), Paris, France, and the B.S. degree in Musicology from the Sorbonne University, Paris, France, in 2011. He received his M.S. degree in acoustics, signal processing, and musical informatics (ATIAM) from the UPMC and the Ircam in Paris, France, in 2013. Since 2013, he is a Ph.D. student at IRCCyN, Nantes, France. His research interests include acoustic scene similarity and classification as well as acoustic scene perception.
% \end{IEEEbiography}
%
%
% \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{figures/anden}}]{Joakim And\'en}
% received the M.Sc. degree in mathematics from the Universit\'e Pierre et Marie Curie, Paris, France, in 2010 and the Ph.D. degree in applied mathematics from Ecole Polytechnique, Palaiseau, France, in 2014. He is currently a postdoctoral researcher with the Program in Applied and Computational mathematics at Princeton University, Princeton, USA. His research interests include signal processing, machine learning, and statistical data analysis. He is a member of the IEEE.
%
% \end{IEEEbiography}
%
% \begin{IEEEbiography}[{\includegraphics[width=1.25in,height=1.25in,clip,keepaspectratio]{figures/lagrange}}]{Mathieu Lagrange} is a CNRS research scientist at IRCCyN, a French laboratory dedicated to cybernetics. He obtained his Ph.D. in computer science at the University of Bordeaux in 2004, and visited several institutions in Canada (University of Victoria, McGill University) and in France (Orange Labs, TELECOM ParisTech, Ircam). His research focuses on machine listening algorithms applied to the analysis of musical and environmental audio.
% \end{IEEEbiography}

>>>>

The \emph{RbQ} measures are compared to commonly used early integration approach \emph{early}, which consists in averaging over time the feature set of each scene, resulting in one feature vector per scene. The distance on this average feature vector is then used to determine $p@k$. For the BOF approach of Aucouturier et al. \cite{aucouturier2007bag}, GMMs are estimated for each scene using the expectation-maximization (EM) algorithm \cite{dempster-laird}. The similarity between a given pair of scene GMMs is then calculated through Monte Carlo sampling approximation. To ensure convergence of the EM algorithm for the scattering features, we reduce their dimension from $1367$ to $30$ by projecting the features onto the top $30$ principal components of the dataset. the number of Gaussians is optimized for each type of features by grid search in the range $[2, 20]$. Best $p@5$ is reached with 8 and 4  Gaussians, respectively for MFCCs and scattering features. Recommended number of Gaussians for MFCCs given in \cite{aucouturier2007bag} is 10.

@@

% \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{figures/lostanlen}}]{Vincent Lostanlen} was born in 1992. He received an engineering degree from TELECOM ParisTech in 2013 and his M.S. degree in acoustics, signal processing, and musical informatics (ATIAM) from the Universit\'{e} Pierre et Marie Curie (UPMC) and the Ircam in Paris, France, in 2013. Since 2013, he is a Ph.D. student at \'{E}cole normale sup\'{e}rieure in Paris, working under the supervision of St\'{e}phane Mallat. His research focuses on defining convolutional operators in the time-frequency domain with applications in audio classification.
% \end{IEEEbiography}
%
% \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{figures/lafay}}]{Gr\'egoire Lafay} was born in 1990. He received the B.S. degree in Acoustic from the University Pierre and Marie Curie (UPMC), Paris, FranArthritis National Research Foundatioce, and the B.S. degree in Musicology from the Sorbonne University, Paris, France, in 2011. He received his M.S. degree in acoustics, signal processing, and musical informatics (ATIAM) from the UPMC and the Ircam in Paris, France, in 2013. Since 2013, he is a Ph.D. student at IRCCyN, Nantes, France. His research interests include acoustic scene similarity and classification as well as acoustic scene perception.
% \end{IEEEbiography}
%
%
% \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{figures/anden}}]{Joakim And\'en}
% received the M.Sc. degree in mathematics from the Universit\'e Pierre et Marie Curie, Paris, France, in 2010 and the Ph.D. degree in applied mathematics from Ecole Polytechnique, Palaiseau, France, in 2014. He is currently a postdoctoral researcher with the Program in Applied and Computational mathematics at Princeton University, Princeton, USA. His research interests include signal processing, machine learning, and statistical data analysis. He is a member of the IEEE.
%
% \end{IEEEbiography}
%
% \begin{IEEEbiography}[{\includegraphics[width=1.25in,height=1.25in,clip,keepaspectratio]{figures/lagrange}}]{Mathieu Lagrange} is a CNRS research scientist at IRCCyN, a French laboratory dedicated to cybernetics. He obtained his Ph.D. in computer science at the University of Bordeaux in 2004, and visited several institutions in Canada (University of Victoria, McGill University) and in France (Orange Labs, TELECOM ParisTech, Ircam). His research focuses on machine listening algorithms applied to the analysis of musical and environmental audio.
% \end{IEEEbiography}
